\documentclass[11pt]{article}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{gensymb}
\usepackage{sectsty}
\usepackage{geometry}
\usepackage[ampersand]{easylist}

\geometry{margin=2cm}

\title{Design Principles and Methods - Navigation Lab Report}
\author{Harley Wiltzer (260690006)\\Juliette Regimbal (260657238)}
\date{October 13, 2016}
\pagenumbering{gobble}
\begin{document}
\maketitle
\pagenumbering{arabic}

\section{Objective}
To design a software system that allows a (main) thread of execution to command it to drive the robot to an absolute position on the field while avoiding obstacles, by use of the odometer and an ultrasonic sensor.
\section{Method}
\begin{easylist}[itemize]
& Using the nagivation tutorial provided, create a class that extends \texttt{Thread} (or, if you want to be very resourceful, a class that implements \texttt{TimeListener}) to control the robot's motors to drive to a specified point on the field, given in Cartesian coordinates. Your class should at least implement the following public methods:
&& \texttt{void travelTo(double x, double y)}\\This method causes the robot to travel to the absolute field location (x, y). This method should continuously call \texttt{turnTo(double theta)} and then set the motor speed to forward(straight). This will make sure that your heading is updated until you reach your exact goal. (This method will poll the odometer for information.)
&& \texttt{void turnTo(double theta)}\\This method causes the robot to turn (on point) to the absolute heading \texttt{theta}. This method should turn a MINIMAL angle to its target.
&& \texttt{boolean isNavigating()}\\This method returns true if another thread has called \texttt{travelTo()} or \texttt{turnTo()} and the method has yet to return; false otherwise.
& Adjust the parameters of your controller, if any, to minimize the distance between the desired destination and the final position of the robot, while simultaneously minimizing the number of oscillations made by the robot around its destination before stopping.
& Write a program to travel to the waypoints (60, 30), (30, 30), (30, 60), and (60, 0) in that order. Test this program ten (10) times, and record the position the robot a) as reported by the odometer, and b) as measured on the field.
& Modify your code to use the ultrasonic sensor to detect an obstacle (a cinder block) and avoid collision with it. You may mount the ultrasonic sensor as you wish, and may use your wall follower code if desired. Additionally, you may create another class to perform this function.
& Write a program to, with obstacle avoidance, travel to the waypoints (0, 60) and (60, 0) in that order. To demonstrate the effectiveness of your obstacle avoidance, the TA will first trun your robot's program to travel that path without obstacles, then place a single cinder block somewhere along the path (though not at a waypoint), and run your robot's program again.
\end{easylist}
\newpage
\section{Data}
\begin{figure}[h!t]
\begin{center}
\caption{Final Position of Robot (cm) - Part 1}
\begin{tabular}{| c | c | c | c | c | c | c |}
\multicolumn{4}{c}{} \\ \hline
Trial No. & x-odometer & y-odometer & x-actual & y-actual & x-error & y-error\\ \hline
1 & 60.92 & -1.80 & 61.8 & 0.4 & -0.88 & -2.20 \\ \hline
2 & 60.84 & -1.52 & 63.0 & -0.2 & -2.16 & -1.32 \\ \hline
3 & 60.61 & -0.87 & 61.9 & 0.5 & -1.29 & -1.31 \\ \hline
4 & 60.88 & -1.51 & 62.2 & -0.3 & -1.32 & -1.21 \\ \hline
5 & 60.94 & -1.66 & 61.5 & -0.7 & -0.56 & -0.96 \\ \hline
6 & 60.86 & -1.58 & 62.4 & -0.4 & -1.54 & -1.18 \\ \hline
7 & 59.92 & 0.20 & 61.0 & 1.6 & -1.08 & -1.40 \\ \hline
8 & 60.60 & -0.65 & 61.2 & 0.3 & -0.60 & -0.95 \\ \hline
9 & 61.04 & -1.86 & 61.5 & -1.2 & -0.46 & -0.66 \\ \hline
10 & 61.08 & -2.04 & 63.0 & -0.2 & -1.92 & -1.84 \\ \hline
Mean & 60.77 & -1.33 & 61.95 & -0.02 & -1.18 & -1.30 \\ \hline
Standard Deviation & 0.34 & 0.69 & 0.70 & 0.77 & 1.37 & 1.44 \\ \hline
\end{tabular}
\end{center}
\end{figure}
\section{Data Analysis}
\subsection{Calculations of Mean and Standard Deviation for Error in Odometer Readings}
\begin{equation}
	\mbox{Mean} = \frac{1}{n} \sum_{k=1}^{n}\mathcal{E}_k
\end{equation}
\begin{equation}
	\mbox{Standard Deviation} = \sqrt{\frac{\sum_{k=1}^{n}\mathcal{E}^2_k}{n-1}}
\end{equation}
In formulae (1) and (2), $n$ represents the number of trials for which data was acquired, and
$\mathcal{E}_k$ represents the error in measurement in some coordinate axis. Below, the calculations
for these values are explicitly shown.
\subsubsection{Calculations of the means}
%\textbf{Mean of Error in Measurement in $x$ Position}
\begin{equation*}
	\begin{aligned}
		\overline{x} &= \dfrac{-0.88-2.16-1.29-1.32-0.56-1.54-1.08-0.60-0.46-1.92}{10}
		&= -1.18 \mbox{cm}
	\end{aligned}
\end{equation*}
\begin{equation*}
	\begin{aligned}
		\overline{y} &= \dfrac{-2.20-1.32-1.31-1.21-0.96-1.18-1.40-0.95-0.66-1.84}{10}
		&= -1.30 \mbox{cm}
	\end{aligned}
\end{equation*}
\subsubsection{Calculations of the standard deviations}
\resizebox{\linewidth}{!}{
	\begin{minipage}{\linewidth}
		\begin{align*}
		s_x &=
		\sqrt{\dfrac{(-0.88)^2+(-2.16)^2+(-1.29)^2+(-1.32)^2+(-0.56)^2+(-1.54)^2+(-1.08)^2+(-0.60)^2+(-0.46)^2+(-1.92)^2}{9}}
		\\
		&= 1.37\mbox{cm}
		\end{align*}
	\end{minipage}
}
\resizebox{\linewidth}{!}{
	\begin{minipage}{\linewidth}
		\begin{align*}
		s_y &=
		\sqrt{\dfrac{(-2.20)^2+(-1.32)^2+(-1.31)^2+(-1.21)^2+(-0.96)^2+(-1.18)^2+(-1.40)^2+(-0.95)^2+(-0.66)^2+(-1.84)^2}{9}}
		\\
		&= 1.44\mbox{cm}
		\end{align*}
	\end{minipage}
}
\subsection{Are the errors present as a result of the odometer or the navigator?}
The errors are caused by both the odometer and the navigator. As seen in the Odometer experiment, there
is significant slippage occuring when the wheels spin. As a consequence of such slippage, there must
be error in the measurement of the $x$ and $y$ position of the robot, as well as in the measurement
of its heading. \\
However, due to the design of the navigator, more error emerges. Since the navigator
must correct its angle continously, one cannot simply tell the navigator to travel some distance in
a given direction. Instead, the navigator is programmed to move on to the next waypoint when it is
within a certain range of the desired target position. Therefore, with this design, error is
inherent and even \textit{allowed}, as a tradeoff for better heading correction. The result is that
while the robot can very accurately reach the waypoint in the appropriate direction, it only gets
to within a certain error margin of the waypoint. These errors, however, are independent from that of
the odometer error. Although the robot may not reach the exact waypoint, the odometer \textit{knows}
the robot has not reached the exact waypoint - that is to say, although there is error in the robots
position due to the design of the navigator, this does not hinder the performance of the odometer.
\\
Furthermore, since the robot is continuously correcting its heading, the wheels undergo a lot of
acceleration (in order to change the robot's direction). Although usually the corrections are very
small, in some situations the corrections may be large enough to cause significant slipping (because
of the acceleration) which can lead to significant error in the odometer readings.

\section{Observations and Conclusion}
\subsection{Explain the operation of the controllers for navigation. How accurately does it move the
robot to its destination? How quickly does it settle on its destination?}
The controller for navigation works by continuously correcting the heading of the robot and having
it move forward until it is within a certain euclidean distance from the waypoint. The heading
correction works by using the waypoint coordinates and the odometer's
readings to calculate by which angle the robot must rotate to be facing its destination. To avoid
constant, tiny corrections (which would result in very jerky behavior and possibly more slippage),
the robot only corrects its heading when it is outside some threshold. This helps the robot settle
quickly on its destination without sacrificing much in terms of accuracy. The robot was observed to
navigate to comfortably within 3 centimeters of its destination in every trial.
\subsection{How would increasing the speed of the robot affect the accuracy of the robot? What is
the main source of error in navigation (and odometry)?}
\section{Further Improvements}

\end{document}
